More flexibility reduces social donations

### 2020-08-18 article-elsevier/article-elsevier.Rmd
Actualización sobre sección del modelo

ggplot(Donaciones_total, aes(x = Fecha , y = monto_FM_UTM)) +
  # Make points small and semi-transparent since there are lots of them
  geom_point(size = 0.5, alpha = 0.5) + 
  # Add vertical line
  #geom_hline(yintercept=1000, linetype="dashed", color = "red") +
  geom_vline(xintercept=as.numeric(as.Date("2010-01-01")), linetype="dashed", color = "red") +
  geom_vline(xintercept=as.numeric(as.Date("2011-01-01")), linetype="dashed", color = "red") +
  geom_vline(xintercept=as.numeric(as.Date("2012-02-08")), linetype="dashed", color = "red") +
  geom_vline(xintercept=as.numeric(as.Date("2016-04-14")), linetype="dashed", color = "red") +
  # Add labels
  labs(x = "Date", y = "Donation to Mixed Found")+
  ylim(0,2500)+
  annotate("text", x = as.Date("2009-08-11"), y = 2000, label = "Law 19885")+
  annotate("text", x = as.Date("2010-01-01"), y = 1850, label = "Law 20316")+
  annotate("text", x = as.Date("2011-01-01"), y = 2000, label = "Law 20565")+
  annotate("text", x = as.Date("2012-02-08"), y = 1850, label = "Law 20900_1")+
  annotate("text", x = as.Date("2016-04-14"), y = 2000, label = "Law 20900_2")+
  ggtitle("Donations: Mixed Found amount over time")

@@

@@

kable(tabla.ley) %>%
  kable_styling(bootstrap_options = "striped")

@@

The model that we create have the next variables

<!-- tabla con variables the modelo -->

and follow the next pannel structure

<!-- ecuación del modelo -->

the result are the following

>>>>

ggplot(Donaciones_total, aes(x = Fecha , y = monto_FM_UTM)) +
  # Make points small and semi-transparent since there are lots of them
  geom_point(size = 0.5, alpha = 0.5) + 
  # Add vertical line
  #geom_hline(yintercept=1000, linetype="dashed", color = "red") +
  geom_vline(xintercept=as.numeric(as.Date("2010-01-01")), linetype="dashed", color = "red") +
  geom_vline(xintercept=as.numeric(as.Date("2011-01-01")), linetype="dashed", color = "red") +
  geom_vline(xintercept=as.numeric(as.Date("2012-02-08")), linetype="dashed", color = "red") +
  geom_vline(xintercept=as.numeric(as.Date("2016-04-14")), linetype="dashed", color = "red") +
  # Add labels
  labs(x = "Date", y = "Donation to Mixed Found")+
  ylim(0,2500)+
  xlim(as.Date("2008-11-30"),as.Date("2019-01-01"))+
  annotate("text", x = as.Date("2009-03-11"), y = 2000, label = "Law 19885")+
  annotate("text", x = as.Date("2010-01-01"), y = 1850, label = "Law 20316")+
  annotate("text", x = as.Date("2011-01-01"), y = 2000, label = "Law 20565")+
  annotate("text", x = as.Date("2012-02-08"), y = 1850, label = "Law 20900_1")+
  annotate("text", x = as.Date("2016-04-14"), y = 2000, label = "Law 20900_2")+
  ggtitle("Donations: Mixed Found amount over time")

@@

tabla.ley$`Median total donation`<-round(tabla.ley$`Median total donation`,2)
tabla.ley$`Median institution donation`<-round(tabla.ley$`Median institution donation`,2)
tabla.ley$`Median Mixed Found donation`<-round(tabla.ley$`Median Mixed Found donation`,2)

@@

kable(tabla.ley) %>%
  kable_styling(bootstrap_options = "striped", position = "center",font_size = 8)

@@

We use a pannel data regression (\ref{eq:1}) in order to study the effect of the change of law on the donations, and follow the next pannel structure

$$\  AI_{i,t}=AMF_{i,t}+AAMF_{i,t}+DL_{i,t}+OD_{i,t}+AAD_{i,t}+AADo_{i,t}+CL_{i}+TD_{i}+DC_{i}+\alpha_{i}+\beta_{t} $$
Where $\ AI_{i,t}$ is the amount of the donation to the institution/foundation of the donor $\ i$ in the year $\ t$, $\ AMF_{i,t}$ is the amount of the donation to the Mixed Found of the donor $\ i$ in the year $\ t$, $\ AAMF_{i,t}$ is the accumulated amount donated to the Mixed Found until that donation (included) of the donor $\ i$ in the year $\ t$, $\ DL_{i,t}$ is a binary variables that take $\ 1$ if the donor $\ i$ in the year $\ t$ has donor more than 1000 UTM, and 0 otherwise, $\ OD_{i,t}$ is and ordinal variable and take the value of the position in the year of the donation of the donor $\ i$ in the year $\ t$, $\ AAD_{i,t}$ is the total accumulated amount (to Mixed Found and to Institutions) of the donor $\ i$ in the year $\ t$ until that donation (included), $\ AADo_{i,t}$ is the accumulated amount of the donee $\ i$ in the year $\ t$ until that donation (included), $\ CL_{i}$ is a binary variable that take value $\ 1$ if the donation is made in the period of validity of the Law 20900, $\ TD_{i}$ is a binary variable that take value $\ 1$ if the donor is a firm and $\ DC_{i}$ is a binary variable that take value $\ 1$ if the donation is made in the period of validity of the digital certification, finally $\ \alpha _{i}$ and $\ \beta _{t}$ control effects by donor and by time

The result are the following
